Holomorphic field theories and higher algebra

### 2022-08-30 draft.tex
unsaved changes
finished subsubsection on funcotrial tfts

\owen{mention some history (e.g., Manin!) and some recent work (CPTVV, Pridham, etc) but then explain our focus: higher analogs of VOAs and finding mathematical analogs of physics}

@@

\subsection{Factorization algebras}

@@

The Weiss covers define a Grothendieck topology on $\Open(M)$, the poset category of open subsets of a space $M$. We call it the {\em Weiss topology} of~$M$. 
Note that Weiss covers are required to ``know'' about every configuration of finitely many points,
and so they often contain many opens.
For a smooth $n$-manifold $M$, one cover is simply to take the collection of open sets in $M$ diffeomorphic to a disjoint union of finitely many copies of the open $n$-disc.

@@

The reader can check by hand that for an ordinary algebra $A$, the value on the circle is $A/[A,A] = {\rm HH}_0(A)$.
This theorem tells us that factorization homology can be seen as a generalization of Hochschild homology,
where one simultaneously generalizes the circle to an arbitrary closed manifold and an algebra to a factorization algebra.

@@

This perspective suggests that factorization algebras offer a natural generalization to field theories on manifolds, and not just on Euclidean spaces. Indeed \cite{CG1, CG2} provide a systematic relationship between field theories and factorization algebras.
The slogan is 
\begin{quote}
the observables of a field theory living on a manifold $M$ form a factorization algebra on~$M$. 
\end{quote}
To physicists, this claim should not be so surprising, upon some reflection:
the Weiss cosheaf gluing axiom offers a precise version of the idea that a quantum field theory can be fully encoded by all its $n$-point functions.

@@

More generally, given a map of Lie groups $G \to O(d)$ and a compatible $G$-action on the theory, a homotopical trivialization of this action on the quantum theory equips $\cA^q$ with the structure of a $G$-framed $E_d$ algebra.

Scheimbauer's thesis then provides a functorial field theory in the sense of Atiyah, Segal, and Lurie.

\begin{thm}
Given a homotopically $SO(d)$-trivial quantization of a classical AKSZ theory on $\RR^d$, 
factorization homology of the quantum observables 
\[
\int_{(-)} \cA^q \colon {\rm Bord}^{or}_d \to {\rm Alg}_d
\]
determines a fully extended oriented $d$-dimensional field theory with values in a higher Morita $(\infty,d)$-category of $E_d$ algebras.
\end{thm}

A similar claim applies to the general case with a map $G \to O(d)$.

>>>>

\owen{mention some history (e.g., Manin! Donaldson-Thomas, Nekrasov) and some recent work (CPTVV, Pridham, etc) but then explain our focus: higher analogs of VOAs and finding mathematical analogs of physics}

@@

\subsection{Meet factorization algebras}

@@

The Weiss covers define a Grothendieck topology on $\Open(M)$, the poset category of open subsets of a space $M$. We call it the {\em Weiss topology} of~$M$. 
Note that Weiss covers are required to ``know'' about every configuration of finitely many points,
and so they often contain many opens.
For a smooth $n$-manifold $M$, a useful Weiss cover is the collection of open sets in $M$ diffeomorphic to a disjoint union of finitely many copies of the open $n$-disc.
(If one has a metric on the manifold, one can work with unions of ``small'' discs.)

@@

This theorem tells us that factorization homology can be seen as a generalization of Hochschild homology,
where one simultaneously generalizes the circle to an arbitrary closed manifold and an algebra to a factorization algebra.

@@

This perspective suggests that factorization algebras offer a natural generalization to field theories on manifolds, and not just on Euclidean spaces. Indeed \cite{CG1, CG2} provide a systematic relationship between field theories and factorization algebras.
The slogan is 
\begin{quote}
the observables of a field theory living on a manifold $M$ form a factorization algebra on~$M$. 
\end{quote}
To physicists, this claim should not be so surprising:
the Weiss cosheaf condition offers a precise version of the idea that a quantum field theory can be fully encoded by all its $n$-point functions.

@@

\subsubsection{Relating to the Atiyah-Segal approach to TFTs}

Atiyah \cite{AtiTFT} offered a mathematical definition for topological field theories that uses symmetric monoidal functors out of bordism categories.
His approach was inspired by Segal's definition of a conformal field theory \cite{SegCFT},
and these notions have subsequently undergone extensive development.
Notably, Baez and Dolan \cite{BaeDol} suggested and advocated for fully extended TFTs; 
their vision was revisited by Lurie \cite{LurieTFT}, who used modern machinery to provide a roadmap for using fully extended TFTs and for proving the cobordism hypothesis.

An important suggestion from \cite{LurieTFT} is that factorization homology allows one to produce nontrivial examples: 
every $E_d$ algebra provides a fully extended $d$-dimensional framed TFT,
albeit taking values in a higher analogue of the Morita bicategory (which works for the $d=1$ case).
Scheimbauer \cite{Scheim} implemented Lurie's suggestion.

\begin{thm}
For any $E_d$ algebra $A$, the functor
\[
\int_{(-)} A \colon {\rm Bord}^{or}_d \to {\rm Alg}_d
\]
determines a fully extended framed $d$-dimensional field theory with values in a higher Morita $(\infty,d)$-category of $E_d$ algebras.
\end{thm}

In combination with the theorem of Elliott and Safronov, we can connect action functionals --- the physicist's usual description of a field theory --- to Atiyah-Segal functorial field theories.

\begin{cor}
For any Lagrangian field theory satisfying the hypotheses of Theorem~\ref{}, 
there is a fully extended framed $d$-dimensional field theory 
given by $\int_{(-)} \cA^q$ where $\cA^q$ denotes the $E_d$ algebra of quantum observables.
\end{cor}

More generally, given a map of Lie groups $G \to O(d)$ and a compatible $G$-action on the theory, 
a homotopical trivialization of this action on the quantum theory equips $\cA^q$ with the structure of a $G$-framed $E_d$ algebra and, by Lurie's work, a $G$-framed fully extended $d$-dimensional TFT.
It is interesting to ask how these kinds of functorial field theories intertwine with the better-known examples.

In this survey we use factorization algebras to capture the rich algebraic structure of holomorphic field theories,
but these connections with functorial TFTs raise the question of producing functorial holomorphic field theories.
